Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-19 Docs/IJES/journal.tex
[A-9] The author/s should explain how the constraint are addressed in GA. What is the meaning of "slack variables"?. Also, they should explain how the solutions are represented, what kind of operators (crossover, mutation, parent selection and offspring selection) used, etc. What is the meaning of "Elite" counter that you have modified from 2 to 50? Are 75 generations enough to ensure the convergence of the GA? The author/s should show the objective function. A similar analysis and/or explanation should be performed for ILP. I think that the author/s should give a more detailed explanation of

The ILP and GA were taken from our previous studies, from~\cite{Trindade2015} and~\cite{Trindade2016}. \textcolor{blue}{Both use slack variables in order to eliminate the modulus operator of Eq.~\eqref{hw-sw-partitioning} and to use commercial tools.} However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout. The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB, as shown in~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$. \textcolor{blue}{All the parameters of ILP and GA algorithms were presented and discussed in~\cite{Trindade2015} and~\cite{Trindade2016}. Choosing ILP and GA, over other possible optimization techniques, it is due to the fact that these techniques were used in related work, as~\cite{Arato2003} and~\cite{Mann2007}, facilitating the comparison with the techniques that we propose in this paper.}

>>>>

The ILP and GA were taken from our previous studies, from~\cite{Trindade2015} and~\cite{Trindade2016}. \textcolor{blue}{Both use slack variables in order to eliminate the modulus operator of Eq.~\eqref{hw-sw-partitioning} and to use commercial tools.} However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout. The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB, as shown in~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$. \textcolor{blue}{All ILP and GA parameters were presented and discussed in~\cite{Trindade2015} and~\cite{Trindade2016}. In particular, the ILP and GA algorithms were chosen since they were also used in other related work, as~\cite{Arato2003} and~\cite{Mann2007}, thus facilitating the comparison to the present techniques (that we propose in this paper).}
